---
title: "Homework 1"
author: Chufeng Yang
output: github_document
---

This is my solution to HM1 and my first R code!

```{r}
library(tidyverse)
```

## Problem 1

Create a data frame 

```{r}
prob1_df =
tibble(
  samp = rnorm(10),
  samp_gt_0 = samp > 0,
  char_vec = c("a","b","c","d","e","f","g","h","i","j"),
  factor_vec = factor(c("red","red","red","green","green","green","blue","blue","blue","blue"))
)
```

Take the mean of each variable in my data frame

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can get the mean of number and logical but not character or factor.

```{r}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert numbers, logical values and factors to numeric but not characters.Logical values can be converted to 1 and 0, and can take a meaningful mean, but character and factor maybe cannot.

Required operation of second code chunk.

```{r}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)))*pull(prob1_df, samp)
```

## Problem 2

This is problem2 about inline R code, plotting and the behavior of ggplot.

```{r}
data("penguins", package = "palmerpenguins")
```

The dataset is about `r names(penguins)`.  
The range of bill length is `r range(pull(penguins,bill_length_mm),na.rm = TRUE)` mm;  
the range of bill depth is `r range(pull(penguins,bill_depth_mm),na.rm = TRUE)` mm;  
the range of flipper length is `r range(pull(penguins,flipper_length_mm),na.rm = TRUE)` mm;  
the range of body mass is `r range(pull(penguins,body_mass_g),na.rm = TRUE)` g;  
the range of year is `r range(pull(penguins, year), na.rm = TRUE)`;  
the levels of species are `r levels(pull(penguins, species))`;  
the levels of island are `r levels(pull(penguins, island))`;  
the levels of sex are `r levels(pull(penguins, sex))`.  

The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length is `r mean(pull(penguins,flipper_length_mm),na.rm = TRUE)` mm.  

Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x), color points using the species variable.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatterplot_penguins.pdf")
```

## HW1 done 
Really learned a lot from HW1 practise !